% ─────────────────────────────────────────────────────────────
% Backbone Ablation Subsection (paste into Section 4 / Experiments)
% ─────────────────────────────────────────────────────────────

\subsection{Backbone Selection Ablation}
\label{sec:backbone_ablation}

To empirically justify the choice of MobileNetV3-Small as the frozen feature
extractor, we compare it against two larger ImageNet-pretrained backbones:
EfficientNet-B0 (5.3\,M parameters, 390\,M FLOPs) and ResNet-18
(11.7\,M parameters, 1\,820\,M FLOPs), using the same 5-fold stratified
cross-validation protocol and identical MLP classifier heads.
All backbones remain \emph{frozen}; only the lightweight MLP is trained.

Table~\ref{tab:backbone_ablation} reports AUC and EER across the three attack
scenarios.  MobileNetV3-Small achieves the highest \emph{average} AUC
(0.917) while being $2.1\times$ smaller and $3.3\times$ faster than
EfficientNet-B0, and $4.7\times$ smaller and $15.3\times$ faster than
ResNet-18.

Notably, both EfficientNet-B0 and ResNet-18 \emph{fail} on text-attack
detection (AUC $\approx$ 0.54--0.56, near chance), whereas MobileNetV3-Small
achieves 0.950.  This suggests that the compact, depth-wise separable
features of MobileNetV3-Small transfer better to fine-grained document
forgery cues---particularly the subtle texture differences introduced by
text manipulation---than the larger but coarser feature maps of EfficientNet
and ResNet.

On the combined (Both) attack, all three backbones perform comparably
(0.944--0.969), likely because the joint face\,+\,text signal provides
enough discriminative information regardless of encoder capacity.  However,
in the critical face-only and text-only scenarios, MobileNetV3-Small is
the only backbone that remains consistently effective, making it the best
choice for a practical, all-scenario deployment.

\begin{table}[t]
\centering
\caption{Backbone ablation study (5-fold stratified CV).  All backbones are
ImageNet-pretrained and \textbf{frozen}; only the MLP head is trained.
Best values per attack are \textbf{bolded}.}
\label{tab:backbone_ablation}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{l r r c c c c c c}
\toprule
 & & & \multicolumn{2}{c}{\textbf{Face Attack}} & \multicolumn{2}{c}{\textbf{Text Attack}} & \multicolumn{2}{c}{\textbf{Both Attack}} \\
\cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
Backbone & Params & FLOPs & AUC$\uparrow$ & EER$\downarrow$ & AUC$\uparrow$ & EER$\downarrow$ & AUC$\uparrow$ & EER$\downarrow$ \\
\midrule
MobileNetV3-S & 2.5\,M & 119\,M & \textbf{0.858\scriptsize$\pm$0.057} & \textbf{20.28\scriptsize$\pm$4.66} & \textbf{0.950\scriptsize$\pm$0.018} & \textbf{11.29\scriptsize$\pm$2.89} & 0.944\scriptsize$\pm$0.029 & 12.79\scriptsize$\pm$3.81 \\
EfficientNet-B0 & 5.3\,M & 390\,M & 0.830\scriptsize$\pm$0.084 & 22.68\scriptsize$\pm$8.78 & 0.539\scriptsize$\pm$0.040 & 47.26\scriptsize$\pm$2.58 & \textbf{0.969\scriptsize$\pm$0.008} & \textbf{9.95\scriptsize$\pm$2.29} \\
ResNet-18 & 11.7\,M & 1\,820\,M & 0.794\scriptsize$\pm$0.098 & 27.27\scriptsize$\pm$7.32 & 0.563\scriptsize$\pm$0.062 & 46.78\scriptsize$\pm$4.36 & 0.947\scriptsize$\pm$0.021 & 11.38\scriptsize$\pm$3.17 \\
\bottomrule
\end{tabular}}
\end{table}

% ─────────────────────────────────────────────────────────────
